---
title: "p8105_hw1_yl4608"
author: "Yutian Luo"
date: "9/19/2020"
output: github_document
---

# 1. Problem 1

## 1.1 Q1
create a data frame comprised of: 
a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”

```{r dataframe}
library(tidyverse)

df = 
  tibble(
    x = rnorm(10),
    vec_logical = x > 0,
    vec_char = c('a','b','c','d','e','f','g','h','i','j'),
    vec_factor = factor(c('low','low','low','low','mod','mod','mod','high','high','high'))
  )

df
```


## 1.2 Q2

take the mean of each variable in your dataframe

```{r mean_dataframe}
mean(pull(df,x))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))

```
1. for logical vectors, automatically coerce the type from logical to 1/0
2. can't take mean for character vectors
3. can't take mean for factor vectors




## 1.3 Q3

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). 

```{r numeric_convert, eval = FALSE}
as.numeric(pull(df,x))
as.numeric(pull(df,vec_logical))
as.numeric(pull(df,vec_char))
as.numeric(pull(df,vec_factor))
```

1. can't convert characters to numeric

## 1.4 Q4

convert the logical vector to numeric, and multiply the random sample by the result
convert the logical vector to a factor, and multiply the random sample by the result
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r convert, eval = FALSE}
as.numeric(pull(df,vec_logical)) * pull(df,x)

as.factor(pull(df,vec_logical)) * pull(df,x)

as.numeric(as.factor(pull(df,vec_logical))) * pull(df,x)

```



# Problem 2

## Q1

Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:

the data in this dataset, including names / values of important variables
the size of the dataset (using nrow and ncol)
the mean flipper length

```{r}
data("penguins", package = "palmerpenguins")
```

The data in this dataset, includes 
`r names(penguins)`
Values of important variables are below:
`r summary(penguins)`

```{r size_dataset, echo = FALSE}
size = nrow(penguins) * ncol(penguins)
```
The size of the dataset is `r size` in penguins.

The mean flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE) ` 


## Q3

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); 
color points using the species variable 

```{r scatter}
ggplot(penguins, mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```


Export your first scatterplot to your project directory using ggsave
```{r export_scatter}
ggsave("scatter_flipperVSBill.pdf",height = 4, width = 6)
```





















